---
title: "COVID Data Analysis"
author: "Jonathan Gilligan"
output:
  github_document: default
---
```{r setup, echo=FALSE, include=FALSE, eval=TRUE}
library(knitr)
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE, include = TRUE)

source("covid-data.R")
startup()
```
# covid-data

<!-- badges: start -->
<!-- badges: end -->

## Description 

This is a collection of R scripts that I use for plotting daily and weekly 
COVID-19 data (case counts and deaths) for counties in the United States.
These scripts use the data collected and curated by the Johns Hopkins 
Center for Systems Science and Engineering (CSSE), which the Center kindly
makes available at <https://github.com/CSSEGISandData/COVID-19>.

To use these scripts, initialize by running the function `startup()`, which 
downloads the latest data from GitHub and prepares it for use.
You can get data for one or more states or counties with 
`select_data()` or `rural_data()`. 

* `select_data()` allows you to specify one or more states or one or more 
  counties within a single state. If you call it with no arguments, it will
  return data for the whole US.
* `rural_data()` allows you to look at data only from rural counties in one or
  more states.
  
* I plot data using `plot_time_series()`, which has a number of options to 
  control the way that the data is plotted.
  
## Examples

Plot weekly COVID-19 deaths for the whole US:
```{r example_1, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
select_data() %>% plot_time_series("deaths")
```

Plot daily new cases for the whole US
```{r example_2, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
select_data() %>% plot_time_series("cases", weekly = FALSE)
```

Plot weekly case data for a single county (Davidson County, TN)
```{r example_county, echo=TRUE, include=TRUE, message=FALSE, warning=FALSE}
select_data("TN", "Davidson") %>% plot_time_series("cases", weekly = TRUE)
```

Make a facet plot for multiple states:
```{r example_facet, message=FALSE, warning=FALSE}
select_data(c("TX", "LA", "MS", "AL", "FL", "GA", "SC", "NC", "TN")) %>%
  plot_time_series("deaths", facet = TRUE)
```

Make a plot for rural counties in several states:
```{r example_rural, message=FALSE, warning=FALSE}
rural_data(c("TX", "LA", "MS", "AL", "FL", "GA")) %>%
  plot_time_series("deaths", weekly = FALSE)
```
